Supplemental material for Tree growth, mortality, and climatic stress in west-coast states, USA

### 2025-10-06 Manuscript.Rmd
The permutation analysis may be in its final form.  The figures 3 and 4 were altered to show MC permutation p-value symbols, and tables were added to the supplemental material to display the actual permuatation p-values.

We obtained empirical means and 95% confidence intervals via bootstrap. For every species we sampled plots with replacement and obtained point estimates.  For each domain we calculated a mean and upper and lower 95% CIs with the 2.5% and 97.5% quantiles from 1000 sampling iterations.  This approach allows for nonsymmetrical CIs around a mean and prevents CIs from including negative values.  We estimated differences between pairs of CWD domains by subtracting within-iteration domain point estimates.

We

@@

```{r diff_grow_fig, fig.height = 6, width = 6, fig.dpi=300, fig.cap=fig.diff_grow, fig.cap.sep=""}

@@

```{r diff_mort_fig, fig.height = 6, width = 6, fig.dpi=300, fig.cap=fig.diff_mort, fig.cap.sep=""}

>>>>

We obtained empirical means and 95% confidence intervals via bootstrap. For every species we sampled plots with replacement and obtained point estimates.  For each domain we calculated a mean and upper and lower 95% CIs with the 2.5% and 97.5% quantiles from 1000 sampling iterations.  This approach allows for nonsymmetrical CIs around a mean and prevents CIs from including negative values.  We estimated contrasts between pairs of CWD domains by subtracting within-iteration domain point estimates.

Our analysis approach results in many comparisons.  We conducted a Monte Carlo (MC) permutation analysis to provide species-level false positive rates. The MC permutation analysis had 1000 iterations; for each iteration the bootstrap sampling was conducted 1000 times.  The domain assignments for each species was sampled without replacement.  The distance of contrast CI bounds from zero were compared against test CI bounds: The permutation recorded a null significant value if the absolute values of the permutation iteration CI bounds were at least as far from zero as observed bounds were.  The false detection rate for a

@@

```{r diff_grow_fig, fig.height = 6.5, width = 6.5, fig.dpi=300, fig.cap=fig.diff_grow, fig.cap.sep=""}

@@

```{r diff_mort_fig, fig.height = 6.5, width = 6.5, fig.dpi=300, fig.cap=fig.diff_mort, fig.cap.sep=""}

### 2025-10-06 Supplemental Material.Rmd
The permutation analysis may be in its final form.  The figures 3 and 4 were altered to show MC permutation p-value symbols, and tables were added to the supplemental material to display the actual permuatation p-values.

source('Global.R')
# Some general analysis info + plots
analysis.stats <- read_rds(paste0(RESULTS.OTHER, "analysis.stats.RDS"))

@@

@@

@@

>>>>

source('Global.R')
source(paste0(CODE.LOC, "Functions.R"))
# Some general analysis info + plots
analysis.stats <- read_rds(paste0(RESULTS.OTHER, "analysis.stats.RDS"))

@@

```{r domain_pvals}

psig.dat2 <- analysis.stats$psig.dat2
psig.g <- psig.dat2[, 1:7]
psig.m <- psig.dat2[, c(1, 8:13)]

psig.ft.g <- psig.ft.fcn(psig.g)
psig.ft.m <- psig.ft.fcn(psig.m)

@@

tbl_psig_growth <- tab_nums(name = "tbl_psiggrowth", 
                            caption = "Monte Carlo permutation p-values for tree species growth domains. Values correspond to Manuscript Figure 3 values.  Values of zero represented no permutation results with confidence intervals equal to or greater than those observed in the data.")

tbl_psig_mort <- tab_nums(name = "tbl_psigmort", 
                            caption = "Monte Carlo permutation p-values for tree species mortality domains. Values correspond to Manuscript Figure 4 values. Values of zero represented no permutation results with confidence intervals equal to or greater than those observed in the data.")

@@

```{r table-psig-growth, tab.cap=tbl_psig_growth}

psig.ft.g

```{r table-psig-mortality, tab.cap=tbl_psig_mort}

psig.ft.m
